---
title: "FoodHygieneReport"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/jamesalsbury/Food-Hygiene-Project")
```

```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(ggplot2)
```

For all of the summary statistics and modelling, I will use the data named All_data_19 Oct_rds, in the folder API_dated. 

## Summary statistics
### Ratings


```{r, echo=FALSE}
establishment_dep_merged = readRDS(file = "data/establishment_dep_merged.rds")
establishment_dep_merged <- establishment_dep_merged %>%
  filter(rating %in% 0:5)
establishment_dep_merged[,12] <- as.numeric(as.character(establishment_dep_merged[,12]))
```

Here are the ratings:

```{r, echo=F}
establishment_dep_merged %>%
  count(rating)
```
We can plot a bar chart of the ratings:


```{r pressure, echo=FALSE}
ratings <- establishment_dep_merged %>%
  count(rating)
  ggplot(data=ratings) + geom_bar(mapping=aes(x=rating, y=n), stat="identity")
```
As we can see, the majority of establishments have a rating of 5 ($\approx$ 71%).

### Types of Establishments
There are 14 different types of establishments, we can see them below with another plot:
```{r, echo=F}
establishment_dep_merged %>%
  count(type)
types <- establishment_dep_merged %>%
  count(type)
  ggplot(data=types) + geom_bar(mapping=aes(x=type, y=n), stat="identity") + theme(axis.text.x = element_text(angle = 90))
```

### NE postcodes
To get a closer view of some local data, I will only consider the establishments with a NExx (Newcastle) postcode.
```{r, echo=F}
NE <- establishment_dep_merged %>%
  filter(postcodeArea=="NE")
NE %>%
  count(rating)
```


